A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-15 method.tex
reversed signs of time slice boundaries
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@619 ccdd05d5-56c1-461a-bf98-85f6876523b4

For concreteness and simplicity, let us consider an inspiral waveform in the quadrupole approximation, for which the time-frequency relation is
\begin{equation}
\label{eq:fgw}
f = \frac{1}{\mathcal{\pi M}} \left[ \frac{5}{256}\frac{\mathcal{M}}{t} \right]^{3/8}.
\end{equation}
Here, $\mathcal{M}$ is the chirp mass of the binary in units of time (where $G M_\odot / c^3 \approx 5 \mu\mathrm{s}$) and $t$ is the time remaining until the coalescence of the binary~\cite{findchirppaper, kidder1992, blanchet2002, hanna2009}. \editorial{Way too many citations here.} Usually the template is truncated at some prescribed time $t = t_0$ before coalescence, often chosen to correspond to the innermost stable circular orbit at which $f = f_\mathrm{ISCO} = 4400 \, M_\odot / M$.  The full template will extend to some low frequency cutoff, $f = f_\mathrm{low}$ corresponding to a time $t_\mathrm{low}$.  This template has a duration of $t_\mathrm{low} - t_\mathrm{0}$ and is critically sampled at a rate of $2 f_\mathrm{isco}$.

@@

If all of these time slices are implemented using the \textsc{fft}, then the latency of this filter bank is $\max_j \left( 2(t_j - t_{j-1}) - t_{j-1} \right) = \max_j \left( 2 t_j - 3 t_{j-1} \right)$.

An example time slice design satisfying these constraints for a $1.4 - 1.4 \, M_{\odot}$ is shown in table~\ref{table:time_slices} below.  For this example, the latency for this time slice design is just $\input{time_slice_latency.tex}$ even if all of the time slices are implemented with the \textsc{fft} method.  This set of time slices will require $\input{time_slice_ops_firslice.tex}$ operations per sample per template, compared with $\input{time_slice_ops_conv.tex}$ for pure \textsc{fft} cross-correlation without time slices, or $\input{time_slice_ops_td.tex}$ for the \textsc{fir} filter method without time slices.

@@

>>>>

For concreteness and simplicity, let us consider an inspiral waveform in the quadrupole approximation, for which the time-frequency relation is
\begin{equation}
\label{eq:fgw}
f = \frac{1}{\mathcal{\pi M}} \left[ \frac{5}{256}\frac{\mathcal{M}}{-t} \right]^{3/8}.
\end{equation}
Here, $\mathcal{M}$ is the chirp mass of the binary in units of time (where $G M_\odot / c^3 \approx 5 \mu\mathrm{s}$) and $t$ is the time relative to the coalescence of the binary~\cite{findchirppaper, kidder1992, blanchet2002, hanna2009}. \editorial{Way too many citations here.} Usually the template is truncated at some prescribed time $t = t_0$, often chosen to correspond to the innermost stable circular orbit at which $f = f_\mathrm{ISCO} \approx 4400 \, M_\odot / M$.  An inspiral signal will enter the \textsc{ligo} band at a low frequency cutoff, $f = f_\mathrm{low}$ corresponding to a time $t_\mathrm{low}$.  This template has a duration of $t_\mathrm{0} - t_\mathrm{low}$ and is critically sampled at a rate of $2 f_\mathrm{isco}$.

@@

If all of these time slices are implemented using the \textsc{fft}, then the latency of this filter bank is $\max_j {\left[-\left( 2(t_j - t_{j-1}) - t_{j-1} \right)\right]} = \max_j \left( 3 t_{j-1} - 2 t_j \right)$.

@@

An example time slice design satisfying these constraints for a $1.4 - 1.4 \, M_{\odot}$ is shown in table~\ref{table:time_slices}.  For this example, the latency for this time slice design is just $\input{time_slice_latency.tex}$ even if all of the time slices are implemented with the \textsc{fft} method.  This set of time slices will require $\input{time_slice_ops_firslice.tex}$ operations per sample per template, compared with $\input{time_slice_ops_conv.tex}$ for pure \textsc{fft} cross-correlation without time slices, or $\input{time_slice_ops_td.tex}$ for the \textsc{fir} filter method without time slices.
